Graphical representation example: Alternative interpretations

### 2023-11-15 notebooks/Graphical_representation_alternatives.Rmd
Versions new case with standard deviations of .5

>>>>

## Case with more predictable results

My expectations were that the representation if the items would be independent
of the covariance matrix, but this has not been the case. I had not predicted
that the item vectors would be "stretched" in space, as has happened, although I
should have expected this because I mention it in the draft, in section 3.3
(Properties of the parameters). Therefore, I acknowledge this representation is
the correct one.

In order to test the prediction that the items are scaled by the standard
deviation, let's test a case that is easier to predict. In order to it, I will
use variances of 0.25, which result in standard deviations of 0.5. Then, if my
understanding of the representation of the vectors is correct, all the vectors
should be scaled by $tfrac{1}{2}$; that is, they should have half the original
length. Their direction however should not change.

```{r define-cov-matrix-prediction}
VARIANCES  <- c(.25, .25)
sd_matrix  <- VARIANCES |> sqrt() |> diag()
cov_matrix <- sd_matrix %*% corr_matrix %*% sd_matrix
```

```{r recompute-oblique-items}
```

```{r item-plot-cov-prediction-out}
#| fig.cap: |
#|   Item plots in an oblique test space, with variances [0.25, 0.25]
plot_oblique + scale_color_manual(values = PALETTE)
```

The resulting MIDSC parameters are effectively half the length, as predicted.
On the other hand, as the MIL is affected by the inverse of the MDICS, the MIL
values are the double of the original ones. This result in vectors that are not
only half the length of the originals. Also, their origin is twice as far from
the origin of the latent space.

## Conclusions

The graphical representation reflects correctly the values of the parameters.
However, the coordinates of the parameters in the latent space do not reflect
the values of the original MCLM parameters.

This is the reason why I understand that a correlation-based representation is
more appropriate.
